Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-07-17 GNproof.tex
changed phrasing of cases to make proof smoother.

Continuing by induction, Since all of $Q_{l-1} \subseteq \cP_{m-1}$ by the induction hypothesis, consider $Q_l \setminus Q_{l-1}$. If this set is empty, we are done. Otherwise, let $q \in Q_l \setminus Q_{l-1}$. By construction $q$ shares support with a propagator in $Q_{l-1}$. Call this propagator $p_j$. Let $v_j$ be the fourth vertex of $p_j$ in the $a_{j}-1$ ordering. Since $I_i(p_j) = a_j$, $v_j$ is not assigned to $I_i$ by $p_j$. We have two cases: $a_j-1 < v_j < j_m$ in any cyclic ordering, or $a_j-1 < j_m < v_j$. (Since $l \neq 0$, we cannot have $v_j = j_m$.) In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.  Since $q$ cannot contribute its fourth vertex, $I_i(q) < v_j < j_m$. That is, $q \in \cP_{m-1}$, giving a contradiction.

Consider the second case ($a_j-1 < j_m < v_j$). {\color{violet}As above, $q$ shares support with $p_j$. More specifically, $a_j \in V(q)$.} By construction, $p_j$ must share support with some $p_r \in Q_{l-2}$. In particular, \hlfix{$a_j \pm 1  = a_r$, otherwise there would be crossing propagators}{The key here is that the contributing end of $p_j$ shares support with the contributing end of $p_r$. Which is on the inside is irrelevant. This is what forces $q$ to be inside both $p_r$ and $p_j$}. If a $q \not \in \cP_m$ is supported on $a_j$ it lies inside $p_j$ in the $a_{j-1}$ ordering. However, for this to happen, and $p_r$ to contribute $a_r$, $q$ must also lie inside $p_r$, which we know by induction cannot happen.

>>>>

Next we prove the base case of $l=1$. Else, let $q \in Q_1 \setminus Q_0$. By construction $q$ shares support with a propagators in $\Q_{0}$. Call this propagator $p_r$. By the above, $p_r \in \cP_{m-1}$. Suppose that $q \not \in \cP_{m-1}$. The violet note above implies that $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.  If $a_j = j_m-1$, such a $q$ cannot exist (it would force $I_i(q) = j_m$). Else, since $q$ cannot contribute its fourth vertex, by Lemma \ref{insert reference}, $I_i(q) < j_m$. That is, $q \in \cP_{m-1}$, giving a contradiction. There are two types of propagators in $Q_1 \setminus Q_0$, the $q$ such that $j_m$ is inside $q$ in the $a_q-1$ ordering, and the $q$ where $j_m$ is on the outside.

Continuing by induction, Since all of $Q_{l-1} \subseteq \cP_{m-1}$ by the induction hypothesis, consider $Q_l \setminus Q_{l-1}$. If this set is empty, we are done. Otherwise, let $q \in Q_l \setminus Q_{l-1}$. By construction $q$ shares support with a propagator in $Q_{l-1}$. Call this propagator $p_r$. Let $v_r$ be the fourth vertex of $p_r$ in the $a_{r}-1$ ordering. Since $I_i(p_r) = a_j$, $v_j$ is not assigned to $I_i$ by $p_j$. We have two cases: there exists a $p_s \in Q_{l-2}$ such that both $p_r$ is on the inside in the $a_s -1$ ordering, and $j_m$ is on the outside, or $p_r$ is on the outside of any $p_s \in Q_{l-2}$ that has $j_m$ on the outside in the $a_s-1$ ordering. In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_s$ in the $a_{s}-1$ ordering.  Since $q$ cannot contribute its fourth vertex, $I_i(q) < v_s < j_m$. That is, $q \in \cP_{m-1}$, giving a contradiction. \sanote{I think this takes care of the picture you sent last night. However, it doesn't address your original complaint about the second case.}

Consider the second case ($a_j-1 < j_m < v_j$). As above, $q$ shares support with $p_j$. More specifically, $a_j \in V(q)$. By construction, $p_r$ must share support with some $p_s \in Q_{l-2}$.
